\chapter{D\lowercase{y}K experiment}
%\section{Overview} depnds how much are the thesis discussed
While ultracold atoms laboratories are in general on the technically heavy side of table-top experiments, the Dy-K machine is a challenging set up even for the standards of the community. While recently the flourishing of ultracold atomic experiments where new, controlled, complexity is added, mostly in the form of \ac{QGM}, use to selectively control individual atoms in lattices or projecting arbitrary potential. The Dy-K set up, while focusing on bulk physics in harmonic traps, proves to be a cumbersome at times.
 For example, a standard ultracold experiment working with an alkali atom in a bulk system, typically uses one or two lasers resonant with the D$2$ and D$1$ lines for cooling, in the \ac{MOT} and grey molasses stages, and one or two high power infrared beam for trapping and evaporative cooling. Working with an heteronuclear mixture requires additional resonant laser sources for the different transitions of the various atomic species \albi{cite}. Moreover, lanthanides atoms like dysprosium, erbium, europium \albi{cite} present a richer electronic structure, which can be used to produce colder sub-\unit{\micro\K} atomic samples before evaporative cooling, as is the case in the Dy-K experiment. \albi{this part to be reduced a bit}
 
 When I joined the team at the end of 2021, the experiment was already fully operational. Many important results regarding the mixture preparation and interaction \cite{Ravensbergen2018ado, Ravensbergen2018poa, Ravensbergen2020rif}, possible upgrades \cite{Kreyer2021mot} and intrinsic limitations \cite{Soave2022lff}, were already successfully achieved. In this chapter, I will first summarize the procedure developed to obtained the doubly-degenerate Fermi mixture \cite{Ravensbergen2018poa,Ravensbergen2020PhD, Tzanova2020PhD}, while in the following section I will describe the results obtained previously concerning  the investigation of interaction in the mixture \cite{Ravensbergen2020rif}.
 
 \section{Experimental sequence at a glance}
In our experiment we use on of the two fermionic isotope of dysprosium, $^{161}$Dy, combined with the only fermionic isotope of potassium, $^{40}$K. We employ an all optical approach to cool the mixture to degeneracy. Due to the different magnetic moments of the two atomic species, the magnetic field gradients applied in the \ac{MOT} are very different, requiring a sequential loading. Since the magnetic gradient used for potassium is about $5$ times stronger than the one needed for dysprosium, it is convenient to first load the K \ac{MOT} and then the Dy one, in order to avoid large losses in the Dy cloud. 

Potassium is loaded in to the $3$D \ac{MOT} from its atomic source, a $2$D \ac{MOT} prepared in a separated glass cell. Both $3$D and $2$D {MOT}s operate on the potassium D$2$ line at \SI{767}{nm} (linewidth $\Gamma_{D2}/2\pi\sim\SI{6}{MHz}$), and all the light beams are generated with the same source\footnote{Toptica TA Pro}. After the \ac{MOT}, potassium is further cooled by performing gray molasses on the D$1$ line (wavelength \SI{770}{nm} with linewidth $\Gamma_{D1}/2\pi\sim\SI{6}{MHz}$), reaching a temperature of around \SI{30}{\micro K}, with an almost ($\sim80\%$) spin polarised sample in the lowest hyperfine state $\ket{9/2,-9/2}$. During the grey molasses cooling, the K cloud is transferred in a large volume reservoir crossed \ac{ODT}, operating in the near infrared at a wavelength of \SI{1064}{nm}\footnote{Azurlight ALS-IR-$1064$-$5$-I-CC-SF}. \albi{add some ref on the general preparation of K in other systems, see also pra cornee}

Once potassium is trapped in the reservoir \ac{ODT}, the preparation of the Dy cloud can start. The dysprosium atomic source is a high-temperature effusion oven operating at around $1000$\,$^\circ$C. The atomic beam is then decelerated using a Zeeman slower, operating along the broad transition at \SI{421}{nm} ($\Gamma_{421}/2\pi\sim\SI{32}{MHz}$). The slowed atomic beam is capture in a $3$D \ac{MOT} generated at the narrow intercombination transition at \SI{626}nm (linewidth $\Gamma_{626}/2\pi\sim\SI{135}{kHz}$). Thanks to narrowness of transition used in the \ac{MOT} the cold atomic sample obtained is already spin polarized in the lowest hyperfine state \cite{Dreon2017oca}, that is the stretched state $\ket{21/2, -21/2}$. At the end of the compressed \ac{MOT} stage, the temperature of the atomic cloud is approximately \SI{8}{\micro K}. After the compressed \ac{MOT} the Dy cloud is also transferred in the same reservoir \ac{ODT} of K.

Before the evaporative cooling stage, necessary to reach the degenerate regime, Dy undergoes an additional resonant cooling\footnote{This additional stage was implemented in the experiment before I joined the team, but reported for the first time in the publication \cite{Ye2022ool}, which is part of this thesis as chapter \ref{Chpt:Lowfieldpaper}.}, performed near the narrow transition at \SI{741}{nm}, with linewidth $\Gamma_{741}/2\pi\sim\,\SI{1.7}{kHz}$ \cite{Lu2011soa}. \albi{maybe there is something regarding the 626 cooling in Paris?} We perform this cooling stage after transferring the atomic clouds in an elongated \ac{ODT}. Thanks to this cooling stage, we manage to reach temperatures around \SI{1}{\micro K} with the Dy cloud. After the cooling stage the mixture is loaded in another cross-\ac{ODT}, also generated at \SI{1064}{nm}\footnote{Mephisto MOPA $18$ NE}, where evaporative cooling takes place. More details on the narrow-line cooling sequence are reported in Sec. \ref{sec:appB}. It is worth noticing here that, while as reported in \cite{Ye2022ool} no effect of the \SI{741}{nm} light are observed on the potassium component, the rapid change in the trap configuration from the reservoir to the elongated configuration strongly affects the potassium cloud, which loses a sizeable amount of atoms. This, as I will discuss soon, does not strictly affect the efficiency of the evaporative cooling, and as not been a limiting factor in most of the experiments presented in this thesis, but reduces  the tunability of the potassium atom number. This limitation and possible solutions are also discussed in Chapter \albi{one of the concluding chapters}.
%sequential loading of the two \ac{MOT}s in a crossed \ac{ODT}. We first  
 
Evaporative cooling in a fermionic experiment requires some extra tricks compared to a bosonic system. The lack of interaction between identical particles prevent the realization of evaporative cooling in a single component atomic cloud. The most 


sysmpathtic cooling for K, with either rubidium \albi{cita Jin et al} and Li has prove very successful \albi{felikx}, despite the wrong mass ration of the two clouds. This approach has been also very successful in the more exotic mixture of Li and Cr, despite requiring an extra step (Feshbach cooling) to achieve complete thermalization. The large dipole moment of highly magnetic atoms like Er and Dy





to facilitate 
 At the end of the \SI{741}{nm} cooling stage, the atomic mixture is trapped in a crossed \ac{ODT} generated at \SI{1064}{nm}. In standard fermionic experiments, evaporative cooling is performed between two spin states of the same atomic species, in order to allow for the interaction necessary for rethermalization. In other heteronuclear fermionic mixture like the LiK  and LiCr experiments,  the typical procedure is to perform evaporative cooling of one of the species, lithium in particular, in two spin states, while the other atomic specie is sympathetic cooled to degeneracy. With highly magnetic atoms, like Dy and Er, quantum degeneracy can be reached in a single spin state, thanks to the \albi{so-called} universal dipolar scattering.
 
 
 In the Dy-K experiment, thanks to the large dipole moment of Dy
 
 
 we can perform evaporative cooling with both species in a single spin state, 
 To facilitate the thermalization process, this trap is formed by two tightly focused beams, an horizontal one with waist \SI{25}{\micro m}, and  a vertical one focused to a waist of \SI{60}{\micro m}. 
 
 universal dipolar scattering for cooling
 
  \albi{table with the different transition and stages of experimental preparation?}




missing ingredient are the interactions

%Due to the intrinsic explorative nature of our experiment, at times, we had aligned on the mixture up to nine infrared beams used for trapping, combined this with two sets of \ac{MOT} beams and two set of molasses beam

\section{Feshbach resonances in D\lowercase{y}-K}



