\chapter{Ultracold Gases and quantum mixtures}
\begin{flushright}{\slshape{
	It is only in very recent times that it has begun to dawn upon\\ the mind of man that there is another world only one degree\\ less complex and wonderful than the stellar universe \\
	-- the world of molecules and atoms } \\ \medskip
	\textnormal{--- Albert A. Michelson \cite{Michelson1896ar}} %\defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974} %For the study of these almost infinitesimal systems of pigmy stars we have no telescope nor even microscope to help us but little by little we are constructing a powerful logical engine which is destined one day to bring the revolutions rotations and oscillations of these minute orbs as clearly to the mind's eye as are now the motions of the worlds of the greater visible universe 
}
\end{flushright}

\section{Why cold atoms?}%colder than the empty universe
%Introduction on the cold atoms field, historically from the MOT to the BEC to the superfluid BEC-BCS crossover. From the first dipolar \ac{BEC} to supersolids to the \ac{mBEC}.


Right at the turn of the 20th century 

why it is so interesting and relevant, great tunabilty, great test field  

Atoms are the most fundamental components that we can control with great precision 

\section{Quantum mixtures}%two is better than one

increase of the possibility to study  

BEC-BCS crossover here


\section{From fermionic spin mixtures to hetero-nuclear mixtures}%



Describe why mass imbalance and some description of the result obtained with other mixtures and describe why Dy-K is our choice 


Zaccanti's varenna notes have a lot of good reference on this

\section{Our choice: Dy-K }

Explorative experimentm, first lanthanide+alkali




 \albi{This works in explaining another advantage (or difference) that comes with using Dy}
Evaporative cooling in a fermionic experiment requires some extra tricks compared to a bosonic system. The lack of interaction between identical particles prevent the realization of evaporative cooling in a single component atomic cloud. In the early years of ultracold fermionic quantum matter two approaches were successfull in cooling to degeneracy an atomic could. The method developed by the group of Debbie Jin at JILA consisted in evaporative cool a bosonic rubidium cloud while sympathetic cooling a sample of fermionic potassium atoms. Thje

The two main approaches are to either use an another atomic species for which efficient evaporative cooling 


sysmpathtic cooling for K, with either rubidium \albi{cita Jin et al} and 


Li has prove very successful \albi{felikx}, despite the wrong mass ration of the two clouds. This approach has been also very successful in the more exotic mixture of Li and Cr, despite requiring an extra step (Feshbach cooling) to achieve complete thermalization. 

The large dipole moment of highly magnetic atoms like Er and Dy


In standard fermionic experiments, evaporative cooling is performed between two spin states of the same atomic species, in order to allow for the interaction necessary for rethermalization. 

In other heteronuclear fermionic mixture like the LiK  and LiCr experiments,  the typical procedure is to perform evaporative cooling of one of the species, lithium in particular, in two spin states, while the other atomic specie is sympathetic cooled to degeneracy. With highly magnetic atoms, like Dy and Er, quantum degeneracy can be reached in a single spin state, thanks to universal dipolar scattering
